%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Modified by : Wei-Chung Hu
% License : MIT
%------------------------

\documentclass[a4paper,11pt]{article}

% Set the page margins.
\usepackage[a4paper,margin=0.75in]{geometry}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{relsize}
\usepackage{graphicx}
\usepackage{CJKutf8}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\qualificationItem}[1]{
  \item{#1 \vspace{-6pt}}
}

\newcommand{\resumeItem}[2]{
  \item{
    \textbf{\small#1}{: \small#2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{ #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeEducationItem}[3]{
  \vspace{-1pt}\item
    {#1}{,}\hspace{4pt}\textit{#2}{,}\hspace{4pt}\textit{#3}\vspace{-6pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand*\bull{\raisebox{-0.365em}[-1em][-1em]{\textscale{4}{$\cdot$}}}
\newcommand*\sbull{\ \ \bull \ \ }

\newcommand\smalldiv{\smash{\raisebox{0.29ex}{\scalebox{0.8}{/}}}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
\begin{CJK}{UTF8}{bkai}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.linkedin.com/in/weichunghu}{\Large Wei-Chung (Victor) Hu \smalldiv 胡維中}} & Email\smalldiv Skype : \href{mailto:selain@nature.ee.ncku.edu.tw}{selain@nature.ee.ncku.edu.tw}\\
  \noindent\href{https://www.linkedin.com/in/weichunghu}{linkedin.com\smalldiv in\smalldiv weichunghu}\sbull
  \href{https://github.com/seLain}{github.com\smalldiv seLain} & Mobile : +886-928-010-215 \\
\end{tabular*}

%-----------Qualification Summary-----------------
\section{Qualification Summary}
  \resumeSubHeadingListStart
      \qualificationItem{Being patient in problem understanding and requirement elicitation. Good at discovering low cost, effective solution by selected tools.}
      \qualificationItem{Initiated evolution of 3 key systems in the former company. Set up POS outsourcing contract and spec.}
      \qualificationItem{Highly interested in building revolutionary, value-delivery social community.}
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Skillset in the Last 2 Years}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: Python, JavaScript}
      \hspace{5pt}
      \textbf{Technologies}{: Django, PyTest, TravisCI, SQLite/MySQL, GitHub}
    }
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {LuckyStrike}{New Taipei City, Taiwan}
      {Freelancer\smalldiv Backend Engineer}{Sept 2017 - Present}
      \resumeItemListStart
        \resumeItem{Consultant}
          {ERP and IT\smalldiv IS consultant of Lee Fong International Group, Macau}
        \resumeItem{Service Backend}
          {Working on a pre-startup project, LuckyStrike. A community to create, advertise and participate commercial lucky draw events. I was responsible for backend part and REST-API construction.}
      \resumeItemListEnd

    \resumeSubheading
      {Lee Fong International Group}{Macau, China}
      {Technical Lead}{Dec 2016 - Aug 2017}
      \resumeItemListStart
        \resumeItem{Web ERP}
          {Introduced and planned a lean Web ERP system by Django for HQ office. The system collects sales data from 6 retail POS and reports HQ managers evidence for CRM, purchasing and marketing decisions.}
        \resumeItem{Secure Data Storage}
          {Built an encrypted, secure storage system based on Python and VeraCrypt. It is used to preserve key documents and databases by SHA-256 encrypted virtual disks and strict access control.}
        \resumeItem{E-Commerce}
          {Customized a new retail website using Prestashop 1.7 and MySQL to increase product visibility over 300\% and enable online ordering. Organized training materials for website operating colleagues.}
        \resumeItem{Outsourcing}
          {Renewed maintenance contract of legacy POS, which was dropped for 30 months before. Set up contract and specification of next-generation POS with a new vendor.}
      \resumeItemListEnd

    \resumeSubheading
      {Database and Software Engineering Lab.}{NCKU, Tainan, Taiwan}
      {Ph.D. Program\smalldiv Research Assistant\smalldiv Engineer}{Sept 2006 - Sept 2016}
      \resumeItemListStart
        \resumeItem{Requirement Enginnering}
          {Built UCFrame, a web framework to collect and elicit requirement from the crowd, with tag system and quality metrics suite designed to collage use cases.}
        \resumeItem{Patents and Award}
          {Led project SIMPLE Touch, a sketch-alive platform for kids developed by Python, OpenCV and Kivy. This project won the 3rd place in 1st ITRI/ASUS AIO competition. 3 TW invention patents, including the sketch-alive process, database design, and device design, were derived from this project.}
        \resumeItem{Teaching Assistant}
          {Maintained SE4PP, a PyGame-based programming learning environment, which was applied in college CS101 for 10 years. Accompanied by: (1) WebHat, an assignment validation system integrating TurboGears, PyLint, Trac, and SVN to create personal working space automatically. (2) SE4PP ELO, a game strategy ranking web by ELO algorithm and prioritized simulation.}
        \resumeItem{Web Enginnering}
          {Maintainer of NCKUEE Webs and founder of NCKUEE Room Reservation System, which were developed by PHP5, Joomla CMS, MySQL.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Side Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Arya}
      {A command-based lightweight kanban based on Python3 and Django. Arya is built for dynamic ticket layout and built-in smart bots in agile process. It's part of my long-term plan in context-aware software engineering.}
    \resumeSubItem{Mattermost\_bot}
      {A chatbot framework for Mattermost cloud messaging. I am a collaborator of this GitHub project in code evolution to support Mattermost APIv4, refactoring, building test cases and resolving issues.}
    \resumeSubItem{Leaf - a Lean ERP and Agent Framework}
      {Based on experience in the former company, I am working on this project to bring out a new, lightweight ERP framework for retail business to modern Django community.}
  \resumeSubHeadingListEnd

%--------Languages------------
\section{Languages}
  \resumeSubHeadingListStart
    \item{
      \textbf{Chinese\smalldiv Mandarin}{: Native}
      \hspace{5pt}
      \textbf{English}{: Limited Working Proficiency}
      \hspace{5pt}
      \textbf{Cantonese}{: Listening}
    }
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeEducationItem
      {Master and Ph.D. of Software Engineering}{National Cheng Kung University}{Taiwan}
    \resumeEducationItem
      {Bachelor of Electrical Engineering}{National Cheng Kung University}{Taiwan}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{CJK}
\end{document}
